---
output: github_document
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# reviewer2r

<!-- badges: start -->
<!-- badges: end -->

The goal of `reviewer2r` is to show a practical example of how to build an R package for the ETL assignment during winter 2021 at the Political Science Department at the Federal University of Pernambuco.

## Installation

You can install the released version of `reviewer2r` 

If for some reason you want to install the released version of `reviewer2r` from [CRAN](https://CRAN.R-project.org) you can do it with:

``` r
install.packages("reviewer2r")
```

Or you can just install development version available on github with:



## Example

This is a basic example which shows you how to use the package:

```{r example}
library(reviewer2r)
```

The main function in the package is the `rev_function`.
It has an argument: `review.` If `review` is `TRUE`, than it returns:

```{r}
rev_function(review = TRUE)
```
On the other hand, when `review` is `FALSE`:

```{r}
rev_function(review = FALSE)
```

